---
title: "Prudential Life Insurance Analysis"
author: "Michael Harrison"
date: "July 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load Libraries
```{r}
library(dtplyr)
library(caret)
library(parallel)
library(doParallel)

seed <- 10
set.seed(seed)
```

#Read in Data
```{r}
train <- read.table("train.csv", sep = ",", header = TRUE)
dim(train)
```

# Columns with NA Values

```{r}
NA.columns <- colnames(train)[colSums(is.na(train))>0]
NA.columns
```

## Check Number of NAs per column
```{r}
NAcolCounts <- colSums(is.na(train))[colSums(is.na(train))>0]
NAcolCounts
```
## Check percentages of NAs in NA Columns; drop columns above threshold

```{r}
NAcolPercentages <- NAcolCounts/(dim(train)[1])
NAcolPercentages
```

- I don't know the feasibility of imputing columns with significant amounts of data missing, especially considering my computation limitations
- Set an arbitrary theshold of 70% NAs present in column to generate a list of columns to remove from the training set

```{r}
NAthreshold <- NAcolPercentages > .7
NAthreshold
```

```{r}
overNAThreshold <- as.list(names(NAthreshold[NAthreshold == TRUE]))
overNAThreshold
```

- Drop the columns that are over the threshold
- Depending on how things shake down with imputing the other columns, may be able to add back the dropped columns - could save on computing issues

```{r}
train.drop <- train[, !(names(train) %in% overNAThreshold)]
```

# Impute the data

## Split Data for NA Handling and Imputation
- First pass on this, I'm going to use the data.table that does not include the columns with NAs above the arbitrary threshold I set above

```{r}
train.imp <- train.drop
train.NA <- train.drop
```

## Impute Data

- Going to try a few methods to impute the data, timing each one to determine how quickly each can be accomplished.

### Mice

- Mice assumes that data is missing at random (MAR). Ideally the threshold set to remove NA heavy columns will leave data that are missing due to randomness
- 
```{r}
library(mice); library(doParallel); library(foreach)
cores <- detectCores() - 1
cluster <- makeCluster(cores)
clusterSetRNGStream(cluster, seed)
registerDoParallel(cluster)

start <- Sys.time()
train.imp <- 
        foreach(no = 1:cores,
                .combine = ibind,
                .export = "train.drop",
                .packages = "mice") %dopar% 
        {
                mice(data = train.drop, m = 3, maxit = 5, method = 'pmm', seed = seed)
        }
stopCluster(cluster)
elapsed.mice <- start - Sys.time()
elapsed.mice
```

```{r}
for(i in 1:3){
        print(colnames(complete(train.imp,i))[colSums(is.na(complete(train.imp,i))>0)])
}
```



# Split Train into Training, Validation, and Testing
- as the testing data set does not have a response column, going to split the test dataset in order to produce validation and test sets that I can measure against

```{r}
set.seed(seed)
train.imp1 <- complete(train.imp, 1)

inTrain <- createDataPartition(train.imp1$Response, p=.60, list = FALSE)
training <- train.imp1[inTrain,]
val.test <- train.imp1[-inTrain,]
inVal <- createDataPartition(val.test$Response, p = .5, list = FALSE)
validation <- val.test[inVal,]
testing <- val.test[-inVal,]
dim(training)
```
```{r}
dim(validation)
```
```{r}
dim(testing)
```


# Response Distribution
```{r}
response.dist <- cbind(freq = table(training$Response), 
                       percentage = prop.table(table(training$Response)) * 100)
response.dist

```

```{r}
mean(response.dist[1:8])
```


# Synthesize Samples
## SMOTE
- Using SMOTE to synthesize under represented samples

```{r, warning=FALSE, message=FALSE}
library(DMwR)

training$Response <- as.factor(training$Response)

set.seed(seed)
start <- Sys.time()
training.smote <- SMOTE(Response~., data = training, 
                        perc.over = 200, perc.under = 100,
                        k = 5)

elapsed.smote <- Sys.time() - start
elapsed.smote
```

```{r}
cbind(freq = table(training.smote$Response), 
      percentage = prop.table(table(training.smote$Response)) * 100)
```



# Column Classes
```{r}
sapply(train, class)
```
## Categorical Variables
```{r}
categorical <- c("Product_Info_1", "Product_Info_2", "Product_Info_3", "Product_Info_5", "Product_Info_6", "Product_Info_7", "Employment_Info_2", "Employment_Info_3", "Employment_Info_5", "InsuredInfo_1", "InsuredInfo_2", "InsuredInfo_3", "InsuredInfo_4", "InsuredInfo_5", "InsuredInfo_6", "InsuredInfo_7", "Insurance_History_1", "Insurance_History_2", "Insurance_History_3", "Insurance_History_4", "Insurance_History_7", "Insurance_History_8", "Insurance_History_9", "Family_Hist_1", "Medical_History_2", "Medical_History_3", "Medical_History_4", "Medical_History_5", "Medical_History_6", "Medical_History_7", "Medical_History_8", "Medical_History_9", "Medical_History_11", "Medical_History_12", "Medical_History_13", "Medical_History_14", "Medical_History_16", "Medical_History_17", "Medical_History_18", "Medical_History_19", "Medical_History_20", "Medical_History_21", "Medical_History_22", "Medical_History_23", "Medical_History_25", "Medical_History_26", "Medical_History_27", "Medical_History_28", "Medical_History_29", "Medical_History_30", "Medical_History_31", "Medical_History_33", "Medical_History_34", "Medical_History_35", "Medical_History_36", "Medical_History_37", "Medical_History_38", "Medical_History_39", "Medical_History_40", "Medical_History_41")

length(categorical)
```

```{r}
for(i in categorical){
        train[,i] <- as.factor(as.character(train[,i]))
}
sapply(train, class)
```




Integer variables have been converted to factors.


## Continuous Variables
```{r}
continuous <- c("Product_Info_4", "Ins_Age", "Ht", "Wt", "BMI", "Employment_Info_1", "Employment_Info_4", "Employment_Info_6", "Insurance_History_5", "Family_Hist_2", "Family_Hist_3", "Family_Hist_4", "Family_Hist_5")

length(continuous)
```


Not sure what to do with these variables.


## Discrete Variables

```{r}
discrete <- c("Medical_History_1", "Medical_History_10", "Medical_History_15", "Medical_History_24", "Medical_History_32")

length(discrete)
```


Not sure how to handle these variables yet.


## Dummy Variables


```{r}
library(mice)
seed <- 7
train_imputed <- mice(train, m=5, maxit = 50, method = 'pmm', seed = seed)
summary(train_imputed)
```




